The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
Report: Layout of benchmarks table

@@

\begin{table}
  \caption{Number of benchmarks used in the \maintrack (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.8]{\begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \midrule
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \bottomrule
  \end{tabular}}
\end{table}

>>>>

\newcommand{\gray}[1]{\textcolor{gray}{#1}}

@@

\begin{table}
  \caption{Number of benchmarks used in the \maintrack (by division). Numbers in brackets indicate the (rounded) percentage of problems with different statuses, which are (sat/unsat) in 2015 and 2016, and (sat/unsat/unknown) in 2017 and 2018.}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.775]{\begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ABVFP & - & - & - & 1 \gray{(0/0/100)}\\
    ALIA & 42 \gray{(2/98)} & 42 \gray{(2/98)} & 42 \gray{(2/98/0)} & 42 \gray{(2/98/0)}\\
    AUFBVDTLIA & - & - & 1709 \gray{(0/1/98)} & 1709 \gray{(0/1/98)}\\
    AUFDTLIA & - & - & 728 \gray{(0/0/100)} & 728 \gray{(0/0/100)}\\
    AUFLIA & 4 \gray{(25/75)} & 4 \gray{(25/75)} & 4 \gray{(25/75/0)} & 4 \gray{(25/75/0)}\\
    AUFLIRA & 19849 \gray{(1/99)} & 19849 \gray{(1/99)} & 20011 \gray{(0/99/1)} & 20011 \gray{(0/99/1)}\\
    AUFNIRA & 1050 \gray{(0/100)} & 1050 \gray{(0/100)} & 1480 \gray{(0/71/29)} & 1480 \gray{(0/71/29)}\\
    BV & 85 \gray{(34/66)} & 85 \gray{(34/66)} & 5151 \gray{(2/2/97)} & 5751 \gray{(10/86/4)}\\
    BVFP & - & - & - & 24 \gray{(0/0/100)}\\
    FP & - & - & - & 61 \gray{(0/0/100)}\\
    LIA & 201 \gray{(5/95)} & 201 \gray{(5/95)} & 388 \gray{(38/60/2)} & 388 \gray{(38/60/2)}\\
    LRA & 339 \gray{(6/94)} & 339 \gray{(6/94)} & 2419 \gray{(17/46/38)} & 2419 \gray{(29/64/8)}\\
    NIA & 9 \gray{(67/33)} & 9 \gray{(67/33)} & 14 \gray{(43/29/29)} & 14 \gray{(43/29/29)}\\
    NRA & 3788 \gray{(0/100)} & 3788 \gray{(0/100)} & 3811 \gray{(0/100/0)} & 3813 \gray{(0/100/0)}\\
    QF\_ABV & 14720 \gray{(68/32)} & 14720 \gray{(68/32)} & 15061 \gray{(69/31/0)} & 15066 \gray{(69/31/0)}\\
    QF\_ABVFP & - & - & - & 18129 \gray{(78/22/1)}\\
    QF\_ALIA & 134 \gray{(40/60)} & 139 \gray{(42/58)} & 139 \gray{(42/58/0)} & 139 \gray{(42/58/0)}\\
    QF\_ANIA & 6 \gray{(0/100)} & 8 \gray{(0/100)} & 8 \gray{(0/100/0)} & 8 \gray{(0/100/0)}\\
    QF\_AUFBV & 37 \gray{(16/84)} & 37 \gray{(16/84)} & 31 \gray{(19/81/0)} & 31 \gray{(19/81/0)}\\
    QF\_AUFLIA & 1009 \gray{(49/51)} & 1009 \gray{(49/51)} & 1009 \gray{(49/51/0)} & 1009 \gray{(49/51/0)}\\
    QF\_AUFNIA & 21 \gray{(29/71)} & 21 \gray{(29/71)} & 17 \gray{(29/71/0)} & 17 \gray{(29/71/0)}\\
    QF\_AX & 551 \gray{(49/51)} & 551 \gray{(49/51)} & 551 \gray{(49/51/0)} & 551 \gray{(49/51/0)}\\
    QF\_BV & 26414 \gray{(35/65)} & 26414 \gray{(35/65)} & 40043 \gray{(32/59/8)} & 40102 \gray{(36/64/0)}\\
    QF\_BVFP & 7 \gray{(14/86)} & 7 \gray{(14/86)} & 17215 \gray{(81/18/0)} & 17215 \gray{(81/18/0)}\\
    QF\_DT & - & - & 8000 \gray{(0/0/100)} & 8000 \gray{(45/55/0)}\\
    QF\_FP & 34413 \gray{(50/50)} & 34413 \gray{(50/50)} & 40302 \gray{(50/50/1)} & 40300 \gray{(50/50/1)}\\
    QF\_IDL & 2094 \gray{(61/39)} & 2094 \gray{(61/39)} & 2193 \gray{(58/37/5)} & 2193 \gray{(58/37/4)}\\
    QF\_LIA & 5839 \gray{(51/49)} & 5839 \gray{(51/49)} & 6141 \gray{(52/46/2)} & 6947 \gray{(55/43/1)}\\
    QF\_LIRA & 6 \gray{(17/83)} & 6 \gray{(17/83)} & 7 \gray{(14/71/14)} & 7 \gray{(14/71/14)}\\
    QF\_LRA & 1626 \gray{(61/39)} & 1626 \gray{(61/39)} & 1649 \gray{(57/41/2)} & 1649 \gray{(57/41/1)}\\
    QF\_NIA & 8475 \gray{(98/2)} & 8593 \gray{(96/4)} & 23876 \gray{(59/13/28)} & 23876 \gray{(59/20/20)}\\
    QF\_NIRA & 2 \gray{(0/100)} & 2 \gray{(0/100)} & 3 \gray{(0/67/33)} & 3 \gray{(0/67/33)}\\
    QF\_NRA & 10184 \gray{(52/48)} & 10245 \gray{(52/48)} & 11354 \gray{(44/47/10)} & 11489 \gray{(44/47/9)}\\
    QF\_RDL & 220 \gray{(49/51)} & 220 \gray{(49/51)} & 255 \gray{(43/44/13)} & 255 \gray{(43/44/13)}\\
    QF\_SLIA & - & - & - & 72705 \gray{(0/0/100)}\\
    QF\_UF & 6649 \gray{(38/62)} & 6649 \gray{(38/62)} & 6650 \gray{(38/62/0)} & 7423 \gray{(42/58/0)}\\
    QF\_UFBV & 31 \gray{(0/100)} & 31 \gray{(0/100)} & 31 \gray{(0/100/0)} & 1224 \gray{(53/47/0)}\\
    QF\_UFIDL & 441 \gray{(24/76)} & 441 \gray{(24/76)} & 428 \gray{(25/75/0)} & 428 \gray{(25/75/0)}\\
    QF\_UFLIA & 598 \gray{(67/33)} & 598 \gray{(67/33)} & 583 \gray{(69/31/0)} & 583 \gray{(69/31/0)}\\
    QF\_UFLRA & 1627 \gray{(48/52)} & 1627 \gray{(48/52)} & 1284 \gray{(60/40/0)} & 1284 \gray{(60/40/0)}\\
    QF\_UFNIA & 7 \gray{(0/100)} & 7 \gray{(0/100)} & 7 \gray{(0/100/0)} & 7 \gray{(0/100/0)}\\
    QF\_UFNRA & 34 \gray{(47/53)} & 34 \gray{(47/53)} & 36 \gray{(58/31/11)} & 36 \gray{(58/31/11)}\\
    UF & 2839 \gray{(28/72)} & 2839 \gray{(28/72)} & 7562 \gray{(10/44/46)} & 7562 \gray{(10/46/44)}\\
    UFBV & 71 \gray{(25/75)} & 71 \gray{(25/75)} & 200 \gray{(34/48/17)} & 200 \gray{(34/48/17)}\\
    UFDT & - & - & 4535 \gray{(0/9/90)} & 4527 \gray{(1/41/58)}\\
    UFDTLIA & - & - & 303 \gray{(0/0/100)} & 303 \gray{(0/0/100)}\\
    UFIDL & 68 \gray{(9/91)} & 68 \gray{(9/91)} & 68 \gray{(4/84/12)} & 68 \gray{(4/84/12)}\\
    UFLIA & 8404 \gray{(0/100)} & 8404 \gray{(0/100)} & 10137 \gray{(0/76/24)} & 10137 \gray{(0/76/23)}\\
    UFLRA & 25 \gray{(20/80)} & 25 \gray{(20/80)} & 15 \gray{(33/67/0)} & 15 \gray{(33/67/0)}\\
    UFNIA & 2319 \gray{(0/100)} & 2319 \gray{(0/100)} & 3308 \gray{(0/74/26)} & 3308 \gray{(0/74/26)}\\
    \midrule
    Total      & 154238 \gray{(40:60)} & 154424 \gray{(40:60)} & 256973 \gray{(37:46:17)} & 333241 \gray{(33:39:28)}\\
    \bottomrule
  \end{tabular}}
\end{table}
